---
title: "Exercise 4"
format: html
editor: visual
---

# Preparation
## Packages
```{r}
## Default repository
local({r <- getOption("repos")
r["CRAN"] <- "http://cran.r-project.org" 
options(repos=r)
})

## Define function check_pkg to tests if package is already installed and hence only needs loading
check_pkg <- function(x)
{
  if (!require(x,character.only = TRUE))
  {
    install.packages(x,dep=TRUE)
    if(!require(x,character.only = TRUE)) stop("Package not found")
  }
}
```

```{r, warning = FALSE, message = FALSE}
## Call check_pkg()
check_pkg("pacman")
check_pkg("dplyr")
check_pkg("ggplot2")
check_pkg("readr")
check_pkg("tidyr")
check_pkg("sf")
check_pkg("terra")
check_pkg("tmap")
check_pkg("zoo")
check_pkg("units")
check_pkg("plotly")
check_pkg("patchwork")
check_pkg("gitcreds")
check_pkg("rjson")
```

# Task 1 + 2 + 3 + 4
I was not able to solve exercises 1-4 because my data looked very different from the example data and I had too much trouble adapting the example code to work with it. I'm using data from Google Timeline, which doesn't have regular timestamps and a description with everything in it (place, time from when to when, distance). 

## Load Data
```{r}
# Read
mittwoch <- st_read(dsn = "data/01.05.24.kml") 
as.data.frame(mittwoch)

# Change to SF object
mittwoch <- mittwoch |>
  st_as_sf(coords = c("E", "N"), crs = 2056, remove = FALSE)
mittwoch

# As dataframe
mittwoch_df <- as.data.frame(mittwoch)
mittwoch_df
```

## Visualize
```{r}
# Filter
walking <- filter(mittwoch, Name == "Walking")
tram <- filter(mittwoch, Name == "On a tram")
bus <- filter(mittwoch, Name == "On a bus")
train <- filter(mittwoch, Name == "On a train")

# Plot
ggplot() +
  geom_sf(data = mittwoch, color = "blue") +
  geom_sf(data = walking, color = "red") +
  geom_sf(data = tram, color = "red") +
  geom_sf(data = bus, color = "red") +
  geom_sf(data = train, color = "red") 
```

# Task 5
```{r}
# Read data
pedestrian <- read_delim("datasets/pedestrian.csv", ",")

```

